Interisland movements and oceanic swimming of woodland caribou in Newfoundland

### 2020-03-20 paper/manuscript.Rmd
minor edits

Regardless, oceanic swimming is relatively common among a minority of
marked caribou. Of the three collared individuals that swam the most, two were collared on
Western Indian Island and the third was collared on Fogo Island. Inter-island
distances between Western and Eastern Indian Islands, and the smaller islands
around them, are shorter than those between Fogo Island and others (Figure 2).
Individuals that were born on or spend more time on these smaller islands may
swim between them more frequently than animals that spend most of their time on
Fogo Island. The forage limitation hypothesis is generally thought to apply
uniformly across populations, but individual caribou could evaluate the costs
and benefits of swimming to another island differently. It is possible that some
individuals, in our case ~10%, considered swimming to be less costly or
perceived competition or predation more acutely than their conspecifics.

>>>>

Oceanic swimming is relatively common among a minority of
marked caribou. Of the three collared individuals that swam the most, two were collared on
Western Indian Island and the third was collared on Fogo Island. Inter-island
distances between Western and Eastern Indian Islands, and the smaller islands
around them, are shorter than those between Fogo Island and others (Figure 2). It is possible that caribou display natal philopatry [@Larue2019] to some of the smaller islands and thus are more likely to  
swim between them more frequently than animals that were born, ospend most of their time, on
Fogo Island. The forage limitation hypothesis is generally thought to apply
uniformly across populations, but individual caribou could evaluate the costs
and benefits of swimming to another island differently. It is possible that some
individuals, in our case ~10%, considered swimming to be less costly or
perceived competition or predation more acutely than their conspecifics.
